\documentclass[00_doc.tex]{subfiles}
\begin{document}
    \section{Class Process}
    \begin{flushleft}
        To teach the class the major concepts of circuits and how to create one with a 
        microcontroller {\footnote{\label{foot: microcontroller} Microcontrollers are 
        extremely small computers that became possible due to the progress of modern 
        micro-technologies. The major difference between computers and microcontrollers 
        is that people can extend the microcontroller by a wide range of sensors that 
        can be used as input or output devices, so it influences the real world around 
        it. \cite{Schief1997, Dembowski2014}}}, the teacher taught the basic principles 
        of Ohm's law, voltage and amper. Furthermore, he thaught the students about how 
        current flows and how to program a microcontroller. Therefore, the teacher 
        showed a circuit simulation and did some live coding sessions. To teach 
        all this, he used multiple sessions.\\~\\

        In the first session, the teacher explained the concept of this class and what 
        the goal of this class is. Therefore, he started to explain current and voltage
        and how current is flowing. In addition, Ohm's law has been presented, so resitors 
        can be explained and introduced. To explain these physics, he showed the students 
        a virtual circuit. With it, he could change the circuit's properties and the 
        circuit response to the changes in real-time.\cite{Wegener2020}\\

        In the second session, he talked about microcontrollers and how these devices can 
        be used. He spent some time explaining the different pins that can be used on an
        Arduino Uno \cite{arduinoUno} like the GND, 5V, 3.3V, A1, D1 or PWM pins and how 
        to program them. To introduce the pins and their functions, he did a live coding 
        session. In this session, he introduced LEDs, humidity and a 
        capacitive sensors. The humidity sensor and capacitive sensor have been drawn with 
        conductive ink.\\

        In the third lecture, he taught the students more about programming, so the code 
        became more complex. He introduced variables and how to define and initiate, and 
        talked about the different data types, and functions like setup and loop and how 
        to read and write current with a microcontroller. In the second half of the class, 
        he introduces Inkscape\cite{inkscape}. With this program, conductive circuits can 
        be created (screenprint). Later he wanted us to find project ideas.\\

        So, every student presented one or multiple ideas in the next meeting and the 
        group discussed those. Sometimes, they discussed how to improve the idea or how 
        this idea can be realized like the material and what kind of sensors has to be
        used. After the discussion with everyone, the classes programmed a bit more, so 
        the students become used to coding and microcontroller. The teacher also 
        introduced arrays and the concepts behind it in this session. \\

        A week later, the class talked and discussed the projects more detailed. This 
        was the final class before anyone started their project. However, nearly 
        everyone attended the class because the teacher gave some tips and helped 
        everyone with their project. In the middle of the semester, every student had 
        to present their project process, and at the end of the class, every student 
        had to present their final prototype. Therefore, every student prepared a 
        presentation and showed their product and its functions. In this presentation, 
        students had to talk about their inspiration for this project, related work, 
        and the user group. Anyone had 10 minutes to talk about these topics. After the 
        presentation, they had an Q\&A session of 5 minutes.
    \end{flushleft}
\end{document}